---
title: "RECS 2015 Codebook"
output:
  html_document:
     css: "style.css"
     toc: true
     toc_depth: 4
     toc_float: true
     self_contained: true
  github_document:
     toc: true
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(janitor)
library(kableExtra)
library(knitr)

recs <- readRDS(here::here("Data", "recs.rds")) %>% 
   haven::zap_labels()
```

The full codebook with the original variables is available at <a href="https://www.eia.gov/consumption/residential/data/2015/index.php?view=microdata" target = "_blank">eia.gov</a>.

## Weighting variables

### DOEID

Unique identifier for each respondent

### NWEIGHT

Final sample weight

### BRRWT

Replicate weights

## Categorical 

### Region

```{r variable-Region}
recs %>%
   count(Region) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: REGIONC

### Division

```{r variable-Division}
recs %>%
   count(Division) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: DIVISION

### MSAStatus

```{r variable-MSAStatus}
recs %>%
   count(MSAStatus) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: METROMICRO

### Urbanicity

```{r variable-Urbanicity}
recs %>%
   count(Urbanicity) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: UATYP10

### HousingUnitType

```{r variable-HousingUnitType}
recs %>%
   count(HousingUnitType) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TYPEHUQ

### YearMade

```{r variable-YearMade}
recs %>%
   count(YearMade) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: YEARMADERANGE

### SpaceHeatingUsed

```{r variable-SpaceHeatingUsed}
recs %>%
   count(SpaceHeatingUsed) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: HEATHOME

### HeatingBehavior

```{r variable-HeatingBehavior}
recs %>%
   count(HeatingBehavior) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: EQUIPMUSE

### ACUsed

```{r variable-ACUsed}
recs %>%
   count(ACUsed) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: AIRCOND

### ACBehavior

```{r variable-ACBehavior}
recs %>%
   count(ACBehavior) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: USECENAC

### ClimateRegion_BA

```{r variable-ClimateRegion_BA}
recs %>%
   count(ClimateRegion_BA) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: CLIMATE_REGION_PUB

### ClimateRegion_IECC

```{r variable-ClimateRegion_IECC}
recs %>%
   count(ClimateRegion_IECC) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: IECC_CLIMATE_PUB

## Continuous

### WinterTempDay

```{r variable-WinterTempDay}
recs %>%
   summarize(Minimum = min(WinterTempDay, na.rm = TRUE),
             Median = median(WinterTempDay, na.rm = TRUE),
             Maximum = max(WinterTempDay, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPHOME

### WinterTempAway

```{r variable-WinterTempAway}
recs %>%
   summarize(Minimum = min(WinterTempAway, na.rm = TRUE),
             Median = median(WinterTempAway, na.rm = TRUE),
             Maximum = max(WinterTempAway, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPGONE

### WinterTempNight

```{r variable-WinterTempNight}
recs %>%
   summarize(Minimum = min(WinterTempNight, na.rm = TRUE),
             Median = median(WinterTempNight, na.rm = TRUE),
             Maximum = max(WinterTempNight, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPNITE

### SummerTempDay

```{r variable-SummerTempDay}
recs %>%
   summarize(Minimum = min(SummerTempDay, na.rm = TRUE),
             Median = median(SummerTempDay, na.rm = TRUE),
             Maximum = max(SummerTempDay, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPHOMEAC

### SummerTempAway

```{r variable-SummerTempAway}
recs %>%
   summarize(Minimum = min(SummerTempAway, na.rm = TRUE),
             Median = median(SummerTempAway, na.rm = TRUE),
             Maximum = max(SummerTempAway, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPGONEAC

### SummerTempNight

```{r variable-SummerTempNight}
recs %>%
   summarize(Minimum = min(SummerTempNight, na.rm = TRUE),
             Median = median(SummerTempNight, na.rm = TRUE),
             Maximum = max(SummerTempNight, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPNITEAC

### TOTCSQFT

Total cooled square footage

```{r variable-TOTCSQFT}
recs %>%
   summarize(Minimum = min(TOTCSQFT, na.rm = TRUE),
             Median = median(TOTCSQFT, na.rm = TRUE),
             Maximum = max(TOTCSQFT, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTHSQFT

Total heated square footage

```{r variable-TOTHSQFT}
recs %>%
   summarize(Minimum = min(TOTHSQFT, na.rm = TRUE),
             Median = median(TOTHSQFT, na.rm = TRUE),
             Maximum = max(TOTHSQFT, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTSQFT_EN

Total square footage (used for publication)

```{r variable-TOTSQFT_EN}
recs %>%
   summarize(Minimum = min(TOTSQFT_EN, na.rm = TRUE),
             Median = median(TOTSQFT_EN, na.rm = TRUE),
             Maximum = max(TOTSQFT_EN, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTUCSQFT

Total uncooled square footage

```{r variable-TOTUCSQFT}
recs %>%
   summarize(Minimum = min(TOTUCSQFT, na.rm = TRUE),
             Median = median(TOTUCSQFT, na.rm = TRUE),
             Maximum = max(TOTUCSQFT, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTUSQFT

Total unheated square footage

```{r variable-TOTUSQFT}
recs %>%
   summarize(Minimum = min(TOTUSQFT, na.rm = TRUE),
             Median = median(TOTUSQFT, na.rm = TRUE),
             Maximum = max(TOTUSQFT, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### CDD30YR

Cooling degree days, 30-year average 1981-2010, base temperature 65F

```{r variable-CDD30YR}
recs %>%
   summarize(Minimum = min(CDD30YR, na.rm = TRUE),
             Median = median(CDD30YR, na.rm = TRUE),
             Maximum = max(CDD30YR, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### CDD65

Cooling degree days in 2015, base temperature 65F

```{r variable-CDD65}
recs %>%
   summarize(Minimum = min(CDD65, na.rm = TRUE),
             Median = median(CDD65, na.rm = TRUE),
             Maximum = max(CDD65, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### CDD80

Cooling degree days in 2015, base temperature 80F (used for garage cooling load estimation only)

```{r variable-CDD80}
recs %>%
   summarize(Minimum = min(CDD80, na.rm = TRUE),
             Median = median(CDD80, na.rm = TRUE),
             Maximum = max(CDD80, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### HDD30YR

Heating degree days, 30-year average 1981-2010, base temperature 65F

```{r variable-HDD30YR}
recs %>%
   summarize(Minimum = min(HDD30YR, na.rm = TRUE),
             Median = median(HDD30YR, na.rm = TRUE),
             Maximum = max(HDD30YR, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### HDD65

Heating degree days in 2015, base temperature 65F

```{r variable-HDD65}
recs %>%
   summarize(Minimum = min(HDD65, na.rm = TRUE),
             Median = median(HDD65, na.rm = TRUE),
             Maximum = max(HDD65, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### HDD50

Heating degree days in 2015, base temperature 50F (used for garage heating load estimation only)

```{r variable-HDD50}
recs %>%
   summarize(Minimum = min(HDD50, na.rm = TRUE),
             Median = median(HDD50, na.rm = TRUE),
             Maximum = max(HDD50, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### GNDHDD65

Heating degree days of ground temperature in 2015, base temperature 65F

```{r variable-GNDHDD65}
recs %>%
   summarize(Minimum = min(GNDHDD65, na.rm = TRUE),
             Median = median(GNDHDD65, na.rm = TRUE),
             Maximum = max(GNDHDD65, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTUEL

Total site electricity usage, in thousand Btu, 2015

```{r variable-BTUEL}
recs %>%
   summarize(Minimum = min(BTUEL, na.rm = TRUE),
             Median = median(BTUEL, na.rm = TRUE),
             Maximum = max(BTUEL, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### DOLLAREL

Total electricity cost, in dollars, 2015

```{r variable-DOLLAREL}
recs %>%
   summarize(Minimum = min(DOLLAREL, na.rm = TRUE),
             Median = median(DOLLAREL, na.rm = TRUE),
             Maximum = max(DOLLAREL, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTUNG

Total natural gas usage, in thousand Btu, 2015

```{r variable-BTUNG}
recs %>%
   summarize(Minimum = min(BTUNG, na.rm = TRUE),
             Median = median(BTUNG, na.rm = TRUE),
             Maximum = max(BTUNG, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### DOLLARNG

Total natural gas cost, in dollars, 2015

```{r variable-DOLLARNG}
recs %>%
   summarize(Minimum = min(DOLLARNG, na.rm = TRUE),
             Median = median(DOLLARNG, na.rmx = TRUE),
             Maximum = max(DOLLARNG, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTULP

Total propane usage, in thousand Btu, 2015

```{r variable-BTULP}
recs %>%
   summarize(Minimum = min(BTULP, na.rm = TRUE),
             Median = median(BTULP, na.rm = TRUE),
             Maximum = max(BTULP, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### DOLLARLP

Total cost of propane, in dollars, 2015

```{r variable-DOLLARLP}
recs %>%
   summarize(Minimum = min(DOLLARLP, na.rm = TRUE),
             Median = median(DOLLARLP, na.rm = TRUE),
             Maximum = max(DOLLARLP, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTUFO

Total fuel oil/kerosene usage, in thousand Btu, 2015

```{r variable-BTUFO}
recs %>%
   summarize(Minimum = min(BTUFO, na.rm = TRUE),
             Median = median(BTUFO, na.rm = TRUE),
             Maximum = max(BTUFO, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### DOLLARFO

Total cost of fuel oil/kerosene, in dollars, 2015

```{r variable-DOLLARFO}
recs %>%
   summarize(Minimum = min(DOLLARFO, na.rm = TRUE),
             Median = median(DOLLARFO, na.rm = TRUE),
             Maximum = max(DOLLARFO, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTALBTU

Total usage, in thousand Btu, 2015

```{r variable-TOTALBTU}
recs %>%
   summarize(Minimum = min(TOTALBTU, na.rm = TRUE),
             Median = median(TOTALBTU, na.rm = TRUE),
             Maximum = max(TOTALBTU, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### TOTALDOL

Total usage, in thousand Btu, 2015

```{r variable-TOTALDOL}
recs %>%
   summarize(Minimum = min(TOTALDOL, na.rm = TRUE),
             Median = median(TOTALDOL, na.rm = TRUE),
             Maximum = max(TOTALDOL, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTUWOOD

Total cordwood usage, in thousand Btu, 2015 (Wood consumption is not included in TOTALBTU or TOTALDOL)

```{r variable-BTUWOOD}
recs %>%
   summarize(Minimum = min(BTUWOOD, na.rm = TRUE),
             Median = median(BTUWOOD, na.rm = TRUE),
             Maximum = max(BTUWOOD, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

### BTUPELLET

Total wood pellet usage, in thousand Btu, 2015 (Wood consumption is not included in TOTALBTU or TOTALDOL)

```{r variable-BTUPELLET}
recs %>%
   summarize(Minimum = min(BTUPELLET, na.rm = TRUE),
             Median = median(BTUPELLET, na.rm = TRUE),
             Maximum = max(BTUPELLET, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```