---
title: "RECS 2015 Codebook"
output:
  html_document:
     css: "style.css"
     toc: true
     toc_depth: 4
     toc_float: true
     self_contained: true
  github_document:
     toc: true
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(janitor)
library(kableExtra)
library(knitr)

recs <- readRDS(here::here("Data", "recs.rds")) %>% 
   haven::zap_labels()
```

The full codebook with the original variables is available at <a href="https://www.eia.gov/consumption/residential/data/2015/index.php?view=microdata" target = "_blank">eia.gov</a>.

## Weighting variables

### NWEIGHT

### BRRWT

## Categorical 

### Region

```{r variable-Region}
recs %>%
   count(Region) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: REGIONC

### Division

```{r variable-Division}
recs %>%
   count(Division) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: DIVISION

### MSAStatus

```{r variable-MSAStatus}
recs %>%
   count(MSAStatus) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```
Variables used: METROMICRO

### Urbanicity

```{r variable-Urbanicity}
recs %>%
   count(Urbanicity) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: UATYP10

### HousingUnitType

```{r variable-HousingUnitType}
recs %>%
   count(HousingUnitType) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TYPEHUQ

### YearMade

```{r variable-YearMade}
recs %>%
   count(YearMade) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: YEARMADERANGE

### YearMade

```{r variable-SpaceHeatingUsed}
recs %>%
   count(SpaceHeatingUsed) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: HEATHOME

### HeatingBehavior

```{r variable-HeatingBehavior}
recs %>%
   count(HeatingBehavior) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: EQUIPMUSE

### ACUsed

```{r variable-ACUsed}
recs %>%
   count(ACUsed) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: AIRCOND

### ACBehavior

```{r variable-ACBehavior}
recs %>%
   count(ACBehavior) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: USECENAC

### ClimateRegion_BA

```{r variable-ClimateRegion_BA}
recs %>%
   count(ClimateRegion_BA) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: CLIMATE_REGION_PUB

### ClimateRegion_IECC

```{r variable-ClimateRegion_IECC}
recs %>%
   count(ClimateRegion_IECC) %>%
   mutate(`Unweighted Freq` = round(n / sum(n), 3)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: IECC_CLIMATE_PUB

## Continuous

### WinterTempDay

```{r variable-WinterTempDay}
recs %>%
   summarize(Minimum = min(WinterTempDay, na.rm = TRUE),
             Median = median(WinterTempDay, na.rm = TRUE),
             Maximum = max(WinterTempDay, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPHOME

### WinterTempAway

```{r variable-WinterTempAway}
recs %>%
   summarize(Minimum = min(WinterTempAway, na.rm = TRUE),
             Median = median(WinterTempAway, na.rm = TRUE),
             Maximum = max(WinterTempAway, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPGONE

### WinterTempNight

```{r variable-WinterTempNight}
recs %>%
   summarize(Minimum = min(WinterTempNight, na.rm = TRUE),
             Median = median(WinterTempNight, na.rm = TRUE),
             Maximum = max(WinterTempNight, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPNITE

### SummerTempDay

```{r variable-SummerTempDay}
recs %>%
   summarize(Minimum = min(SummerTempDay, na.rm = TRUE),
             Median = median(SummerTempDay, na.rm = TRUE),
             Maximum = max(SummerTempDay, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPHOMEAC

### SummerTempAway

```{r variable-SummerTempAway}
recs %>%
   summarize(Minimum = min(SummerTempAway, na.rm = TRUE),
             Median = median(SummerTempAway, na.rm = TRUE),
             Maximum = max(SummerTempAway, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPGONEAC

### SummerTempNight

```{r variable-SummerTempNight}
recs %>%
   summarize(Minimum = min(SummerTempNight, na.rm = TRUE),
             Median = median(SummerTempNight, na.rm = TRUE),
             Maximum = max(SummerTempNight, na.rm = TRUE)) %>%
   kbl() %>%
   kable_minimal()
```

Variables used: TEMPNITEAC
