---
title: "Categorical Data Analysis Exercise Solutions"
output:
  html_document:
    df_print: paged
---

# Set-up
```{r setup}
library(tidyverse) # for tidyverse
library(here) # for file paths
library(survey) # for survey analysis
library(srvyr) # for tidy survey analysis

anes <- read_rds(here("Data", "anes_2020.rds")) %>%
   mutate(Weight=Weight/sum(Weight)*231592693) 
# adjust weight to sum to citizen pop, 18+ in Nov 2020 per ANES methodology documentation
anes_des <- anes %>%
   as_survey_design(weights = Weight,
                    strata = Stratum,
                    ids = VarUnit,
                    nest = TRUE)
```

# Part 1

1. How many females have a graduate degree? Hint: the variables `Gender` and `Education` will be useful.

```{r ex1_1}


```


2. What percentage of people identify as "Strong democrat"? Hint: The variable `PartyID` indicates what party people identify with.

```{r ex1_2}

```



3. What percentage of people who voted in the 2020 election identify as "Strong republican"? Hint: The variable `VotedPres2020` indicates whether someone voted in 2020.

```{r ex1_3}

```

4. What percentage of people voted in both the 2016 election and in the 2020 election?  Include the logit confidence interval. Hint: The variable `VotedPres2016` indicates whether someone voted in 2016.

```{r ex1_4}

```

5. What is the design effect for the proportion of people who voted early? Hint: The variable `EarlyVote2020` indicates whether someone voted early in 2020.

```{r ex1_5}

```

# Part 2

1. Is there a relationship between PartyID and whether people voted early?

```{r ex2_1}

```


2. Is there a relationship between PartyID and trust in the government? Hints: `TrustGovernment` indicates how strongly people trust the government. Use Wald as the `statistic` option.

```{r ex2_2}

```


# Bonus

1. What percentage of people lean republican? These are individuals that are strong republicans, not very strong republicans and are independent-republicans. Include an appropriate confidence interval. Hint: to get the correct confidence interval, create a new variable BEFORE calculating the estimate.

```{r exb_1}

```

2. Were people who lean democrat more likely to vote early in the 2020 election? Hint: use a logistic model and 3-level party variable to use in the model.

```{r exb_2}

```
