---
title: "Design objects and derived variables exercise"
output:
  html_document:
    df_print: paged
---

# Course set-up

First, let's make sure you have everything you need for the course. Run the following library statements. If something is not installed, install it.

```{r setup}
# install.packages("tidyverse")
# remotes::install_github("bschneidr/r-forge-survey-mirror")
# install.packages("srvyr")
# install.packages("here")
# install.packages("palmerpenguins")
# install.packages("remotes")

library(tidyverse) # for tidyverse
library(here) # for file paths
library(srvyr)


```

# Part 1 - Design Objects

In these exercises, you will be given a study and assume you have the data. How would you create the design object?

1.  California Health Interview Survey - 2019-2020
    -   Note that you can do this with design variables aka Taylor's series or replicate weights.
    -   Useful links:
        -   <https://healthpolicy.ucla.edu/chis/design/Pages/methodology.aspx>
        -   <https://healthpolicy.ucla.edu/chis/analyze/Pages/sample-code.aspx>
        -   <https://healthpolicy.ucla.edu/chis/analyze/Pages/weighting.aspx>
    -   Assume you have the Public Use File for **adults** already read into R and the dataframe is called `chis19_adult`.

```{r chis, eval=FALSE}
chis19_adult <- haven::read_sas(here::here("RawData", "adult_2019_sas", "adult.sas7bdat"))

```

2.  National Survey on Drug Use and Health - 2019
    -   Useful links:
        -   <https://www.datafiles.samhsa.gov/dataset/national-survey-drug-use-and-health-2019-nsduh-2019-ds0001>
        -   <https://www.datafiles.samhsa.gov/dataset/national-survey-drug-use-and-health-2019-nsduh-2019-ds0001>
    -   Assume you have the Public Use File for already read into R and the dataframe is called `nsduh19`.

```{r nsduh, eval=FALSE}
nsduh19 <- haven::read_sav(here::here("RawData", "NSDUH_2019", "NSDUH_2019.SAV"))

```


# Part 2 - Derived variables

Before exercises, read the data in
```{r datin, cache=TRUE}
anes <- read_rds(here("Data", "anes_2020.rds"))
recs_in <- read_csv(here("RawData", "RECS_2015", "recs2015_public_v4.csv"))
```

In these exercises, you will be given specifications for a derived variable. Create the variable and check your work. Useful resources:

- [ANES Codebook Raw Variables](https://electionstudies.org/wp-content/uploads/2022/02/anes_timeseries_2020_userguidecodebook_20220210.pdf)
- [ANES Codebook Exiting Derived Variables](https://github.com/tidy-survey-r/tidy-survey-short-course/blob/main/Codebook/ANES-2020-Derived-Variable-Codebook.md)
- [RECS Codebook Raw Variables](https://www.eia.gov/consumption/residential/data/2015/xls/codebook_publicv4.xlsx) - Note this will download a spreadsheet

1. ANES: Create a 5-level income variable as described below. For cases where the income is refused or the interview was a breakoff, this derived variable should be `NA`. The variable should be created such that "Under $25,000" comes first and so on. Hint: Use the variable `V201617x`

   - Under $25,000
   - $25,000-49,999
   - $50,000-74,999
   - $75,000-99,999
   - $100,000 or more
   
```{r income5}

```
   
2. ANES: Create a 5-level age variable as described below. For the cases where age is refused, this derived variable should be `NA`. Hint: use variable `V201507x`

   - 18-24
   - 25-44
   - 45-64
   - 65-74
   - 75 or older
   
   
```{r age5}

```

3. RECS: Create a logical variable indicating whether there was any household energy insecurity. Household energy insecurity is defined as households that have any of the following occur at least once:

- Reducing or forgoing basic necesseties to pay energy costs (SCALEB)
- Leaving home at unhealthy temperature (SCALEG)
- Receiving disconnect or delivery stop notice (SCALEE)
- Unable to use heating equipment (NOHEATBROKE, NOHEATEL, NOHEATNG, NOHEATBULK)
- Unable to use cooling equipment (NOACBROKE, NOACEL)

The relevant variables that should be used are included in parentheses.

```{r energyinsec}

```

