---
title: "Warm-up Exercise Solutions"
output:
  html_document:
    df_print: paged
---

# Course set-up
First, let's make sure you have everything you need for the course. Run the following library statements. If something is not installed, install it.

```{r setup}
# install.packages("tidyverse")
# remotes::install_github("bschneidr/r-forge-survey-mirror")
# install.packages("srvyr")
# install.packages("here")
# install.packages("palmerpenguins")
# install.packages("remotes")

library(tidyverse) # for tidyverse
library(here) # for file paths
library(palmerpenguins)


```

# Warm-up exercises for Day 1

```{r datapeek}
glimpse(penguins)
```

How many penguins of each species are there? Hint: use `count`

```{r speciestab}
penguins %>%
   count(species)
```

How many penguins of each species and sex are there? Hint: use `count`

```{r speciessextab}
penguins %>%
   count(species, sex)
```

What is the proportion of each species of penguins? Hint: use `count` then `mutate` 

```{r speciestabp}
penguins %>%
   count(species) %>%
   mutate(
      p=n/sum(n)
   )
```

What is the proportion of each sex of penguins within species? Hint: use `count` then `group_by` and `mutate` 

```{r speciessextabp}
penguins %>%
   count(species, sex) %>%
   group_by(species) %>%
   mutate(
      p=n/sum(n)
   )

```

# Warm-up exercises for Day 2

What is the mean body mass in grams of all penguins? Hint: use `summarize` and remove missing data

```{r peng_meanmass}
penguins %>%
   summarize(
     MeanBodyMass=mean(body_mass_g, 
                       na.rm=TRUE)
     )
```

What is the mean length of flipper by species? Hint: use `group_by`

```{r peng_meanflip_species}
penguins %>%
   group_by(species) %>%
   summarize(
     MeanFlipperLength=mean(flipper_length_mm, 
                            na.rm=TRUE)
     )
```

What is the mean flipper length by species and sex?

```{r peng_meanflip_speciessex}
penguins %>%
   group_by(species,sex) %>%
   summarize(
     MeanFlipperLength=mean(flipper_length_mm, 
                            na.rm=TRUE))
```

Fit a simple linear regression between body mass and flipper length.

```{r pengLM}
#Option 1
mod1 <- lm(body_mass_g ~ flipper_length_mm, data=penguins)
summary(mod1)

#Option 2
mod2 <- glm(body_mass_g ~ flipper_length_mm, data=penguins)
summary(mod2)
```


# Session information

```{r si}
devtools::session_info(pkgs="attached")
```