---
title: "Warm-up Exercises"
output:
  html_document:
    df_print: paged
---

# Course set-up
First, let's make sure you have everything you need for the course. Run the following library statements. If something is not installed, install it.

```{r setup}
# install.packages("tidyverse")
# remotes::install_github("bschneidr/r-forge-survey-mirror")
# install.packages("srvyr")
# install.packages("here")
# install.packages("palmerpenguins")
# install.packages("remotes")

library(tidyverse) # for tidyverse
library(here) # for file paths
library(palmerpenguins)


```

# Warm-up exercises for Day 1

```{r datapeek}
glimpse(penguins)
```

How many penguins of each species are there? Hint: use `count`
```{r speciestab}

```

How many penguins of each species and sex are there? Hint: use `count`

```{r speciessextab}

```


What is the proportion of each species of penguins? Hint: use `count` then `mutate` 

```{r speciestabp}

```

What is the proportion of each sex of penguins within species? Hint: use `count` then `group_by` and `mutate` 

```{r speciessextabp}

```


# Warm-up exercises for Day 2

What is the mean body mass in grams of all penguins? Hint: use `summarize` and remove missing data

```{r peng_meanmass}

```

What is the mean length of flipper by species? Hint: use `group_by`

```{r peng_meanflip_species}

```

What is the mean flipper length by species and sex?

```{r peng_meanflip_speciessex}

```

Fit a simple linear regression between body mass and flipper length.

```{r pengLM}

```

