---
title: "Target Population 2020 ANES"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Target pop 2020 ANES
From the User Guide: "The target population for the fresh cross-section was the 231 million non-institutional U.S. citizens aged 18 or older living in the 50 US states or the District of Columbia."

- We will use Current Population Survey (CPS) to find this total from November 2020
- Relevant data dictionary: https://www2.census.gov/programs-surveys/cps/datasets/2020/basic/2020_Basic_CPS_Public_Use_Record_Layout_plus_IO_Code_list.txt

```{r}
library(censusapi)
library(tidyverse)

cps_state_in <- getCensus(
   name="cps/basic/nov",
   vintage=2020,
   region="state",
   vars=c("HRHHID", "HRMONTH", "HRYEAR4", "PRTAGE", "PRCITSHP", "PWSSWGT"),
   key = Sys.getenv("CENSUS_API_KEY")
)

cps_state <- cps_state_in %>%
   as_tibble() %>%
   mutate(across(.fns=as.numeric))

# confirm this doesn't include territories
cps_state %>%
   count(state)

# confirm this is only November 2020
cps_state %>% 
   count(HRMONTH, HRYEAR4)

# voting age citizen population

targetpop <- cps_state %>% 
   as_tibble() %>%
   filter(
      PRTAGE>=18,
      PRCITSHP %in% (1:4)
   ) %>%
   pull(PWSSWGT) %>%
   sum()



```

The target population in 2020 is: `r prettyNum(targetpop, big.mark=",")`.


## Target pop 2016 ANES
From the User Guide: "...and the target population for the Internet mode was 224.1 million U.S. citizens age 18 or older living in the 50 US states or the District of Columbia"

- We will use Current Population Survey (CPS) to find this total from November 2016

```{r}

cps_state_in <- getCensus(
   name="cps/basic/nov",
   vintage=2016,
   region="state",
   vars=c("HRHHID", "HRMONTH", "HRYEAR4", "PRTAGE", "PRCITSHP", "PWSSWGT"),
   key = Sys.getenv("CENSUS_API_KEY")
)

cps_state <- cps_state_in %>%
   as_tibble() %>%
   mutate(across(.fns=as.numeric))

# confirm this doesn't include territories
cps_state %>%
   count(state)

# confirm this is only November 2016
cps_state %>% 
   count(HRMONTH, HRYEAR4)

# voting age citizen population

targetpop <- cps_state %>% 
   as_tibble() %>%
   filter(
      PRTAGE>=18,
      PRCITSHP %in% (1:4)
   ) %>%
   pull(PWSSWGT) %>%
   sum()



```

The target population in 2016 is: `r prettyNum(targetpop, big.mark=",")`.

